---
title: "theCLT"
author: "Gael Gonzalez"
date: 'Summer 2022'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")
print(mean(KK_data))
print(sd(KK_data))
```



Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

It is not unimodal because of the multiple peaks and it has 2 peaks. The peaks are not the same size. Our standard deviation is 41.7 and the mean is 50.

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

It appears to me that............ It is not unimodal because of multiple peaks and it has 3 peaks. 2 peaks are the same size and one is bigger.

The standard deviation is 29.2 and the new mean is 50.1

Do this again for 4 random samples

```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
print(mean(x.avg))
print(sd(x.avg))
```

It is not unimodal because of multiple peaks and it has 3 peaks. Every peak are different sizes. 

The standard deviation is 20.8 and the new mean is 50.9

Then again for 9 random samples

```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
print(mean(x.avg))
print(sd(x.avg))
```

It is not unimodal because of multiple peaks and it has 2 peaks. The 2 peaks are different sizes. 

The standard deviation is 14 and the new mean is 49.1

then 16 random samples

```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
print(mean(x.avg))
print(sd(x.avg))
```

It is unimodal because of the single peak and it has one peak. The peak is one size, so yes they are all the same size.

The standard deviation is 10.3 and the new mean is 50.4

finally for 36 random samples.

```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
print(mean(x.avg))
print(sd(x.avg))
```

It is unimodal because of the single peak and it has one peak. The peak is one size, so yes they are all the same size.

The standard deviation is 6.8 and the new mean is 50.

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

The middle of the graph where the peak seems to be more heavily populated then the outsides of the graph. The population data seems to be more centralized as the sample size grew.

Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 

Then submit the link to your github project  to canvas to complete this assignment.